The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-04-03 paper.tex
paragraph on tejas' paper explaining why we subtract the monopole

In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
an interferometer like the OVRO LWA with lots of short baselines, a sensible choice is to use all
spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
is determined by the maximum baseline length of the interferometer.  For an interferometer without
short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
determined by the minimum baseline length.  When creating the maps presented in this paper, we use
$l_\text{min} = 0$ and $l_\text{max} = 1000$.
\todo{exclude l = 0 and cite tejas' paper}

>>>>

In practice we now need to pick the set of spherical harmonics we will use to represent the sky. For
an interferometer like the OVRO LWA with lots of short baselines, a sensible choice is to use all
spherical harmonics with $l\le l_\text{max}$ for some $l_\text{max}$. The parameter $l_\text{max}$
is determined by the maximum baseline length of the interferometer.  For an interferometer without
short spacings, a minimum value for $l$ might also be used. This $l_\text{min}$ parameter should be
determined by the minimum baseline length.  When creating the maps presented in this paper, we use
$l_\text{min} = 0$ and $l_\text{max} = 1000$.

The interferometer's sensitivity to $l=0$, however, deserves special consideration.
\citet{2016ApJ...826..116V} prove -- under fairly general assumptions -- that an interferometer is
only sensitive to the monopole of the sky brightness if there exists some form of cross-talk or
common-mode noise pick-up. In fact, the sensitivity of the interferometer is proportional to the
amplitude of these effects. For consistency we will include $a_{00}$ while solving
Equation~\ref{eq:m-mode-matrix-equation} for the vector $\b a$, but we set $a_{00} = 0$ afterwards
because we do not have a measurement of cross-talk or common-mode noise pick-up.
